---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(hablar) ## retype()
library(zoo)
library(hash)
library(dict)
library(dplyr)
library(lubridate)
library(tsibble)
if (!require("devtools")) install.packages("devtools")
devtools::install_github("mkuhn/dict")
```

```{r}
d = read_excel("CNTSDATA.xlsx")
military <-read_excel("CNTSDATA2.xlsx")

## creating a hashmap from header and column names
hm <- data.frame(row.names = names(d), val = names(military))

## creating a dictionary to map header names and column names
hm_dic <- dict()
#hm_dic[c(row.names(hm))] <- hm$val
hm_dic[c(hm$val)] <- row.names(hm)


## Remove columns with more than 50% NA
mil <- military[, which(colMeans(!is.na(military)) > 0.5)]
```

```{r}
n = read.csv("nuclear.csv")
```

```{r}
mil1 <- na.locf(mil[c(1:35,37:82, 84,88:120)])
clean_mil <- retype(na.locf(mil1))
write.csv(clean_mil,"data.csv", row.names = FALSE)
```

```{r}
full <- merge(x=clean_mil, y=n, by.x=c("country","year"), by.y =c("Entity","Year") )
write.csv(full,"data_with_nuclear.csv", row.names = FALSE)
```

### Correlations

```{r}
## constructing a dataframe of correlations
alpha <- data.frame(t(cor(full$military1, full[c(5:115)])))

## column renaming
colnames(alpha) <- c("corr")

## filtering out absolute correlation > 0.9
high_cors <- alpha %>% filter(abs(corr) > 0.9)

## storing the columns of higly correlated values as a list
high_cors_names <- c(row.names(high_cors))
```

```{r}
## printing header names of highly correlated columns
for (val in high_cors_names) {
  print(hm_dic[[val]])
}
```

```{r}
hm_dic[c(high_cors_names)]
```




## Splitting the data country-wise
```{r}
military_df <- read.csv("military_df.csv")
```

```{r}
library(tsibble)
rows <- "Entity == 'China'"
china_df <- military_df %>% filter(Entity == "China") %>%
            select(Miliary_exp_mil, Year) %>%
            as_tsibble(index = Year)
class(china_df)
```

### Line plot of military expenditure of China
```{r}
china_df %>%
  autoplot(Miliary_exp_mil) +
  labs(title= "China Military expediture", y = "$US")
```


```{r}
library(utils)
library(astsa)
library(dplyr)
library(tsibble)
library(tidyverse)
library(fpp3)
library(GGally)
library(sugrrants)
library(xts) 
dcmp <- china_df %>%
  model(stl = STL(Miliary_exp_mil))
components(dcmp) %>% autoplot()
```
## Train-test split
```{r}
train = china_df %>%slice(1:28)
test = china_df %>%slice(n()-4:0)
```

```{r}
acf(train$Miliary_exp_mil)
```

Each spike that rises above or falls below the dashed lines is considered to be statistically significant. (Chapter 16 talks about this in detail.) This means the spike has a value that is significantly different from zero. If a spike is significantly different from zero, that is evidence of autocorrelation. A spike that's close to zero is evidence against autocorrelation.

This also means that the data is not stationary.



```{r}
train %>%
  autoplot(difference(Miliary_exp_mil)) +
  labs(title= "China Military expediture", y = "$US")
```
differencing the time series tends to make it stationary.

### Augmented Dickey-Fuller Test

```{r}
library(tseries)
adf.test(na.locf(difference(difference(china_df$Miliary_exp_mil))))
```
- differencing the time series twice resulted in stationary hypothesis.

```{r}
train <- train %>%
  mutate(diff2 = difference(difference(train$Miliary_exp_mil)))
```


```{r}
library(caret)
library(forecast)
fit <- train %>%
  model(trend_model = TSLM(Miliary_exp_mil ~ trend()))
chn_fc <- fit %>% forecast(h = "6 years")

accuracy(chn_fc$.mean, test$Miliary_exp_mil)

chn_fc %>% autoplot(china_df)
```


```{r}
acf(diff(china_df$Miliary_exp_mil))
```

differencing the time series tends to make it stationary.

```{r}
library(tseries)
adf.test(na.locf(difference(difference(china_df$Miliary_exp_mil))))
```



```{r}
exp <- as_tsibble(china_df %>%
  select(Miliary_exp_mil)) %>%
  update_tsibble(index = Year, regular = TRUE)
```

```{r}
china_diff_exp <- exp %>%
  mutate(diff_exp = difference(Miliary_exp_mil))
```


```{r}
fit <- china_diff_exp %>%
  model(mean_model = MEAN(diff_exp))

fit %>% forecast(h = '2 year') %>%
  autoplot(china_diff_exp)
```










